---
title: DSA8023 Analytathon 1
subtitle: Data Cleaning
author: Abraham Wilson
date: '`r format(Sys.Date())`'
output: html_document
---

```{r}
library(readxl)
library(kableExtra)
library(DT)
```

To begin with the processing the dataset provided, we will need to merge the two workbook documents provided to us. These excel file are available in the data/raw folder.

Below, we will merge the two excel files into one big excel file and convert it to csv for easier processing. To do this, we will need to import the two files.

```{r}
energia_data_1 <- read_xlsx("C:/Projects/Analytathon1/data/raw/WB1_Energia_Challenge_March_2023_Data.xlsx", sheet = 2)
energia_data_2 <- read_xlsx("C:/Projects/Analytathon1/data/raw/WB2_Energia_Challenge_March_2023_Data.xlsx", sheet = 2)

write.csv2(rbind(energia_data_1, energia_data_2), "C:/Projects/Analytathon1/data/processed/Energia_Challenge_March_2023_Data_Merged.csv", row.names = FALSE)
```

```{r}
energia_data_complete <- read.csv2("C:/Projects/Analytathon1/data/processed/Energia_Challenge_March_2023_Data_Merged.csv")

dim(energia_data_complete)
```

You can see that we have successfully merged the two datasets using the `rbind()`.

Now let us use the `datatable()` from the DT package along with the `head()` to see the first 50 rows of the combined data file.
```{r}
datatable(head(energia_data_complete, n = 50), options = list(scrollX = TRUE))
```

